### 2016-03-17 Draft.tex
Ensure the file compiles

\begin{figure}[h!]\centering
\includegraphics[width=0.68\textwidth]{Hazards.pdf}
\caption{\label{HazardFxns}  Examples of instantaneous rates of detection (hazard functions) from exponential, gamma, lognormal, and Weibull TTDDs. \jarad{Are these setup to have the same mean and variance or anything like that?}
\end{figure}

@@

\jarad{Again, I would introduce this without covariates or random effects first.

>>>>

\begin{figure}[h!]\centering
\includegraphics[width=0.68\textwidth]{Hazards}
\caption{Examples of instantaneous rates of detection (hazard functions) from exponential, gamma, lognormal, and Weibull TTDDs. \jarad{Are these setup to have the same mean and variance or anything like that?}}
\label{HazardFxns}
\end{figure}

@@

\jarad{Again, I would introduce this without covariates or random effects first.}
